%Peter's Part
\textbf{Peter Dang}\newline
Some strengths that I possess would be some Embedded and Electrical Hardware skills that I can put on the table. I am pretty comfortable with the Embedded Systems work while continually working with students as a T.A. I can also contribute a little bit as a Scrum Master since I am quite familiar with everybody in the group, and can exchange information with others to meet deadlines.
\newline
\newline
%Matt's Part
\textbf{Matt Draft}\newline
I am well organized, motivated and detail oriented. I am comfortable with many different technologies such as python, raspberry pi, aurdiuno and others which may come in handy for this project. (we should probably all get together to discuss what roles exist and who should be responsible for what)
\newline
\newline
%Eddie's Part
\textbf{Eddie Molina}\newline
I am familiar with embeddeed systems programming, and can build and solder circuits together. I am mechanically inclined and can put together a system that will require valves, pumps, and pipe 
connections which will be useful for this project. I can also research equipment pricing in order
to stay within budget restraints.
\newline
\newline
%Marco's Part
\textbf{Marco Paramo}\newline
My strengths will be in developing and testing software. I am comfortable with many different programming languages and am constantly learning more about them in order to make more stable code. Some past projects I have worked on have been creating a chat room, many IRC chat bots, and video games. Being able to create simple and efficient solutions to problems is what I strive to do in any project I work on.
\newline
\newline
%Van's Part
\textbf{Van Ta}\newline
Throughout my college career, I worked on many group projects with various restrictions, resulting in me being adaptable to most random problems. I have learned a few programming languages and had some experiences with embedded systems like the arduino microcontroller or a custom ABET alarm system. I know a majority of the group members, so I believe we will work very well together. 
\newline
\newline
%Robert's Part
\textbf{Robert Villazana}\newline
My strengths include hardware programming, such as embedded systems, and soldering and wiring things up. I am also comfortable in programming in C and Python. I also have a little bit of knowledge in front-end web development. 
\newline
\newline